Different forms of uncertainty differently affect the evolution of social learning

### 2022-08-13 ms.tex
minor revision to analysis

First, we confirmed the current theoretical understanding that greater $u$ uniformly decreased
$\meansl$ across all other uncertainty parameter values. The other uncertainty
parameters changed the $u$ value at which $\meansl$ began to decrease,
and how rapidly $\meansl$ decreased over $u$. 
For example, when payoff ambiguity and selection set size were
both small ($\pilow = 0.1$ and $B=2$), social learning evolved only when $u$ was
small. 
% These parameter settings present a relatively easy problem for individuals.
% Furthermore, it is relatively costly for agents to be misled by outdated social 
% information in this case, especially for longer lifespans for finding the 
% optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily over $u$ due to 
drift caused by weak selection caused by little advantage for performing the optimal versus
non-optimal behavior (see rows of Figure~\ref{fig:mainResults}). We analyzed several
such patterns of social learning evolution and suppression across different uncertainty settings.

@@

\begin{itemize}
  \item 
    We tested two additional settings of the softmax behavior selection
    greediness parameter, $\beta=0.01,1.0$, which reproduced qualitative patterns in
    the evolution of social learning. 
  \item
    We see that certain details are changed within this broad agreement between
    results obtained with different $\beta$. 
    \begin{enumerate}
      \item 
        More drift when $\beta=1$, which can be seen in certain $(\pilow, B)$ pairs
        (entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}b). 
        For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
        data points with greater drift, i.e., where $\meansl \approx 0.5$. 
    \end{enumerate}
\end{itemize}

>>>>

First, we confirmed existing theoretical predictions that greater $u$
uniformly decreased $\meansl$ across all other uncertainty parameter values.
The other uncertainty parameters changed the $u$ value at which $\meansl$
began to decrease, and how rapidly $\meansl$ decreased over $u$.  For example,
when payoff ambiguity and selection set size were both small ($\pilow = 0.1$
and $B=2$), social learning evolved only when $u$ was small. 
% These parameter settings present a relatively easy problem for individuals.
% Furthermore, it is relatively costly for agents to be misled by outdated
% social information in this case, especially for longer lifespans for finding
% the optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily
over $u$ due to drift caused by weak selection caused by little advantage for
performing the optimal versus non-optimal behavior (see rows of
Figure~\ref{fig:mainResults}). We analyzed several such patterns of social
learning evolution and suppression across different uncertainty settings.

@@
